---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# aucvar

<!-- badges: start -->
<!-- badges: end -->

The goal of aucvar is to calculate the variance of AUC through different estimators,
including an unbiased variance estimator, bootstrap variance estimator, and jackknife
variance estimator.

## Installation

You can install the development version of aucvar from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("fmoyaj/aucvar")
```

## Example

This is a basic example which shows you how to calculate the variance of the AUC
using an unbiased estimator:

```{r example}
library(aucvar)
mydata <- na.omit(breastcancer) # Omit NA values
optimal_model <- glm(Class~`Clump Thickness`+`Uniformity of Cell Shape`+
      `Bare Nuclei` + `Bland Chromatin`, family=binomial(link="logit"), data=mydata)
predictions <- predict(optimal_model, type="response")
varAUC(predictions, mydata$Class, 10^3)
```

You can also calculate the AUC for a logistic regression model
```{r example2}
library(aucvar)
mydata <- na.omit(breastcancer) # Omit NA values
optimal_model <- glm(Class~`Uniformity of Cell Shape`
                         , family=binomial(link="logit"), data=mydata)
prob <- predict(optimal_model, type="response")
labels <- mydata$Class
auc(prob, labels)
```

